# pre-class


Make sure you commit this often with meaningful messages. 



```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


1. Read the source code for each of the following three functions, puzzle out what they do, and then brainstorm better names.

```{r}
#Takes a string and a prefix and check to see if the prefix is part of the string. If yes, then True, if no, False for each character in the string. 
Check_for_prefix <- function(string, prefix) {
  substr(string, 1, nchar(prefix)) == prefix
}

check_for_prefix(c(1,12,3,4), 12)

```

```{r}
#Remove the last item
remove_last <- function(x) {
  if (length(x) <= 1) return(NULL)
  x[-length(x)]
}

remove_last(c(1,2,3,4,5))
```

```{r}
#Repeat the pattern of the y vector so that it is the same length as the vector x.
Repeat_second_until_same_length_as_first <- function(x, y) {
  rep(y, length.out = length(x))
}

Repeat_second_until_same_length_as_first(c(1,2,3,4,5), c(2,3,3,4))
```

2. Compare and contrast rnorm() and MASS::mvrnorm(). How could you make them more consistent?
```{r}
#According to R help section, rnorm() is the function for normal distribution where the mean = 0, sd=1. 


#MASS::mvrnorm()is simulate from a multivariate normal distribution that produces one or more samples from the specified multivariate normal distribution. It takes n, mu, Sigma. 


```

3. Use `lapply()` and an anonymous function to find the coefficient of variation (the standard deviation divided by the mean) for all columns in the mtcars dataset. 
```{r}
lapply(mtcars, function(x) sd(x)/mean(x))
```
4. Use vapply() to:
    a. Compute the standard deviation of every column in a numeric data frame.
    b. Compute the standard deviation of every numeric column in a mixed data frame. (Hint: you’ll need to use vapply() twice.)

```{r}
vapply(df, sd, numeric(1))

vapply(df(vapply[df,is.numeric, logical(1)]), sd, numeric(1))
```
